### 2019-04-08 7_conclusion.tex
Taking Alex's suggestion for the conclusion.

Task Bench is a promising new approach for evaluating the performance
of parallel and distributed programming systems. We have seen that
systems with support for asynchronous (and/or task-based) programming
appear to show benefits with more complicated dependency patterns,
higher node counts (because of higher communication latencies) and
more communication (because of ability to overlap it with
computation). However, all these benefits can be eclipsed if baseline
runtime overheads are too high. The current generation of task-based
systems (PaRSEC, Realm, Regent, and StarPU) show higher overheads
than traditional HPC systems, indicating that there continues to be
work to be done in this area.

>>>>

Task Bench is a promising new approach for evaluating the performance
of parallel and distributed programming systems. We have seen that
systems vary by orders of magnitude in runtime overhead, as measured
by METG. Widely used systems in industry have METG measured in
seconds, reflecting the very coarse tasks and lack of need for strong
scaling performance in current workloads. At the other extreme,
traditional HPC systems have METG in the range of 10-100 \textmu{}s,
necessary for strong scaling to small task granularities. The newer
task-based systems, with METG in the range of 100 \textmu{}s to 1 ms
have performance sufficient for weak scaling many HPC workloads, but
more work is needed to strong scale the most demanding applications.
